Untitled

### 2020-08-26 psychsci_wordcount.Rmd
added research highlights, video transcripts

---
title             : "Understanding the impacts of video-guided activities on parent-child interaction"
shorttitle        : "Impacts of videos on parent-child interaction"

author: 
  - name          : "George Kachergis"
    affiliation   : "1"
    address       : "Stanford, CA 94305 USA"
    email         : "kachergis@stanford.edu"
  - name          : "Emily Hembacher"
    affiliation   : "1"
  - name          : "Veronica Cristiano"
    affiliation   : "2"
  - name          : "Hanwen Vivian Zhang"
    affiliation   : "3"
  - name          : "Michael C. Frank"
    corresponding : yes
    address       : "Stanford, CA 94305 USA"
    email         : "mcfrank@stanford.edu"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"
  - id            : "2"
    institution    : "Gallaudet University"
  - id            : "3"
    institution    : "Cornell University"

abstract: |
  Early parenting practices play an important role in shaping children’s future outcomes. 
  In particular, high-quality early interactions can facilitate language learning and school performance. 
  The rise of phone-based parenting applications ("apps") could deliver low-cost interventions on parenting style to a wide variety of populations, especially the parents of very young children, who are often difficult to reach in other ways. 
  Yet little is known about the effects of communicating to parents through app-based interventions. 
  In two studies (one preregistered), we showed parents short videos depicting age-appropriate parent-child activities from a parenting app. 
  We found that after watching the video, parents spoke more and made more bids for joint attention, as compared with controls who watched no video (experiment 1) or a science video (experiment 2). 
  These results suggest that activity videos can lead to positive changes in parent engagement, providing support for the use of such videos in parenting interventions.
keywords          : "language development; parent intervention; childhood development; joint attention; lexical diversity"
wordcount         : "4954"
bibliography      : ["library.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
header-includes:
  - \usepackage{float}
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=4, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=T, 
                      message=F, sanitize = T)
```

```{r setup, include = FALSE}
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(papaja)
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(psych)
library(langcog)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)
library(tidyboot)
library(knitr)
library(rstanarm)
library(bayestestR)
source("multiplot.R")

select <- dplyr::select # masked by MASS
theme_set(theme_few())

# labels=addline_format(c("Activity Video", "Science Video"))
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}
```

```{r load-exp1-lexical-data, include=F}
e1path = "../parenting_obs_e1/"

d = read.csv("../language_analyses/exp1_lexical_diversity.csv")

e1_parent_ed = table(d$parent_ed)

e1ld <- d %>%
  mutate(condition = factor(condition), 
         gender = as.factor(gender),
         video = as.factor(video))

e1_gender = table(e1ld$gender)

# rate calculations (tokens / min, words / min)
e1_play_duration <- read.csv(paste0(e1path,"joint_attention/parenting_obs_play_duration_E1.csv"), header=T)
e1_play_duration$start_sec = with(e1_play_duration, ifelse(is.na(verbalcue_start_sec), 
                                                           play_start_sec, verbalcue_start_sec))
e1_play_duration <- e1_play_duration %>% 
  mutate(play_duration = (play_stop_sec - start_sec) / 60) %>% # sec to mins
  select(SID, play_duration)
e1ld <- e1ld %>% left_join(e1_play_duration, by=c("sid"="SID"))

# convert types and tokens to rate: types/min and tokens/min
e1ld <- e1ld %>% 
  mutate(types = (types / play_duration), 
         tokens = (tokens / play_duration),
         TTRnorm = (TTR / play_duration), # # not really interpretable if we normalize LD measures
         MTLDnorm = (MTLD / play_duration)
         )

e1_6to12 = table(subset(e1ld, age<1)$condition) # con 9, exp 10
e1_12to18 = table(subset(e1ld, age<1.5 & age>=1)$condition) # con 11 exp 9
e1_18to24 = table(subset(e1ld, age>=1.5)$condition) # con 10, exp 11
```

```{r load-exp1-joint-attention-data, echo=F}
load(paste0(e1path,"joint_attention/Exp1_joint_attention_data.RData"))
d$Condition <- factor(d$Condition, levels = c("con","exp"), labels = c("No Video","Activity Video"))

e1ja <- d %>%
  #filter(!is.na(AA), !is.na(EL), !is.na(RR)) %>% # 6 parents NA -- don't want to remove from main analysis!
  mutate(Condition = factor(Condition), 
         bids_tot = as.numeric(bids_tot),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         parent_ed = langcog::scale(parent_ed, scale=TRUE),
         gender = as.factor(gender),
         Video = as.factor(Video)
         #pja_length = pja_length/1000,
         #cja_length = cja_length/1000,
         #total_lja = total_lja/1000
         ) # convert duration ms -> seconds
```

```{r load-exp2-lexical-data, echo=F}
e2path = "../parenting_obs_e2/"
load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
e2Age <- d %>% mutate(Age = age) %>%
  select(sid, Age)
e2_parent_ed = table(d$parent_ed) # unscaled parent_ed
d = read.csv("../language_analyses/exp2_lexical_diversity.csv")
d <- d %>% left_join(e2Age, by="sid")

e2ld <- d %>%
  mutate(condition = as.factor(condition), 
         gender = as.factor(gender),
         video = as.factor(video)) %>%
  select(-X.1, -X)

e2ld$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Science Video", "Activity Video"))

e2_gender = table(d$gender)
e2_12to18 = table(subset(d, Age<1.5)$Condition) # Activity Vid 20, Science Vid 21
e2_18to24 = table(subset(d, Age>=1.5)$Condition) # Activity Vid 22, Science Vid 21

#e2_dur = read.csv(paste0(e2path,"joint_attention/parenting_obs_play_duration_E2.csv"))
#e2_dur <- e2_dur %>% mutate(vid_dur=video_duration_sec / 60) %>% # sec / min
#  select(sid, vid_dur)
#e2ld <- e2ld %>% left_join(e2_dur, by="sid")

e2_play_duration <- read.csv(paste0(e2path,"joint_attention/parenting_obs_play_duration_E2.csv"), header=T)
e2_play_duration$start_sec = with(e2_play_duration, ifelse(is.na(verbalcue_start_sec), 
                                                           play_start_sec, verbalcue_start_sec))
e2_play_duration <- e2_play_duration %>% 
  mutate(play_duration = (play_stop_sec - start_sec) / 60) %>% # sec to min
  select(sid, play_duration)
e2ld <- e2ld %>% left_join(e2_play_duration, by="sid")

# convert types and tokens to rate: types/min and tokens/min
e2ld <- e2ld %>% 
  mutate(types = (types / play_duration), 
         tokens = (tokens / play_duration),
         TTRnorm = (TTR / play_duration), # not really interpretable if we normalize LD measures
         MTLDnorm = (MTLD / play_duration)
         )
```

```{r load-exp2-joint-attention-data, echo=F}
load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Science Video","Activity Video"))
d$Age = d$age 
e2ja <- d %>% mutate(bids = bids,
                     age = as.numeric(langcog::scale(age, scale=FALSE))
                     #pja_length = pja_length/1000,
                     #cja_length = cja_length/1000,
                     #total_lja = total_lja/1000
                     ) # convert duration ms -> seconds

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

@@

## Method

### Participants. 
`r nrow(e1ld)` infants (F = `r e1_gender['F']`, M = `r e1_gender['M']`) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in northern California. 
We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2). 
62% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent. 
Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5). 
Fifteen parents reported that their child was of Hispanic origin. 
Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = `r e1_parent_ed[1]`), some college (n = `r e1_parent_ed[2]`), four-year college (n = `r e1_parent_ed[3]`), some graduate school (n = `r e1_parent_ed[4]`), to completed graduate school (n = `r e1_parent_ed[5]`).

### Materials.
Stimuli included activity videos from a commercial parenting application. 
The videos were designed to show activities to parents that they could perform with their child in order to foster cognitive and physical development, and were targeted to the child's age and level of development. 
In each video, an adult and child perform the activity (e.g., sorting toys according to size) while a narrator explains the activity and its purpose. 
We selected two videos for each of three age groups in our sample (6-11.9 months, 12-17.9 months, 18-23.94 months).
Participants were also given a set of toys corresponding to those in the video that they watched so that they could complete the activity.[^1]

[^1]: Details of the specific videos used and the toys associated with each video are in the Appendix.

Participants were randomly assigned to either the *Activity Video* condition or the *No Video* condition. 
Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2020]. 
The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment ([see SI](https://osf.io/2bpdf/?view_only=69c0c6ca5d2649438e8642a57671ba79)).

### Procedure.
After providing informed consent, parents in the Activity Video condition watched the assigned activity video on a laptop with headphones.
To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played. 
Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed. 
The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of approximately three minutes.[^2]
In the No Video condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
They were not given any additional instructions about how to use the props.

In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless Shure lavalier microphone to record their child-directed speech. 
After three minutes of play had elapsed, parents were told they could stop playing and the cameras and microphone were turned off.
Parents were then asked to complete the EPAQ before being debriefed.

### Joint Attention Coding Procedure.
The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software [@datavyu]. 
The video taken at floor level was coded by default, but the other video was referred to if the participants were occluded or if there was technical difficulty with the first camera. 
Each session's video was coded for episodes of coordinated JA, episodes of passive JA, and parental bids for JA. 
Parental bids for JA were defined as any attempt to initiate joint attention (i.e labeling, pointing, or otherwise drawing attention to an object) that did not result in passive or coordinated JA. 
If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
An episode of joint attention was considered _passive_ if both participants visually focused on an object for 3 or more seconds but the child did not acknowledge the parent. 
If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same episode of joint attention. 
A joint attention episode was considered _coordinated_ if both participants visually focused on an object for 3 or more seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking. 
Full details of our guidelines for coding joint attention are available in SI.

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55, 0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95% CI = [-0.11, 0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 95% CI = [0.32, 0.85] for rate of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11, 0.67] for time spent (seconds per minute) in passive JA episodes, and ICC = 0.60 with 95% CI = [0.24, 0.82] for time spent in coordinated JA episodes.

## Results

Parents' child-directed speech during the play sessions (mean duration: `r round(mean(e1ld$play_duration), 2)` min) was transcribed; child utterances were not considered.
Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2[^3], with any deviations or exploratory analyses noted.
Below we first report the lexical diversity results, followed by the joint attention results.

[^3]: Preregistration: [https://osf.io/6k9m8/](https://osf.io/6k9m8/?view_only=d4b230deba2a4f91bdb2aba29088d982)

### Lexical Diversity

For each transcript of child-directed speech, the caregivers' unique word *types* and *tokens* (total words) uttered were tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity. 
Although we initially preregistered TTR as our measure of lexical diversity (since it is a simple, commonly used measure), it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010]. 
Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (we use 0.72, as proposed by McCarthy & Jarvis).

```{r, e1-lexdiv-regressions, echo=F, include=F}
# get estimated coefficient and 89% CI from Bayesian regression
get_stan_glmer_reporting_values <- function(model, cond, digits=2) {
  ci95 <- posterior_interval(model, prob = 0.95, pars = cond)
  ci89 <- posterior_interval(model, prob = 0.89, pars = cond) # 89% CIs as recommended by Kruschke and others
  pd = p_direction(model)
  pd = pd[which(pd$Parameter==cond),]$pd
  ci = round(c(ci95,ci89,pd), digits)
  names(ci) = c("95pLB","95pUB","89pLB","89pUB","pd") # 95% and 89% lower and upper bounds
  beta = round(model$coefficients[cond], digits)
  return(c(beta,ci))
}

print_CI <- function(mod) {
  string = paste0("89% CI = [",mod['89pLB'],", ",mod['89pUB'],"]", ", *pd* = ",mod['pd'])
  return(string)
}

modTTR <- stan_glmer(TTR ~ condition * age + (1|video), data=e1ld, adapt_delta = .97)
summary(modTTR) # ESS from ~1800 - 3600
p_direction(modTTR, effects="all") # condition
e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.11

modMTLD <- stan_glmer(MTLD ~ condition * age + (1|video), data=e1ld)
summary(modMTLD) # ESS ~ [2200, 4100]
p_direction(modMTLD, effects="all") # condition
e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") # -8.48

# predict word tokens
tokens_mod <- stan_glmer(tokens ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld) 
summary(tokens_mod)
p_direction(tokens_mod, effects="all") # condition
e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 19.45

# predict word types
types_mod <- stan_glmer(types ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld,
                        adapt_delta = .97)
summary(types_mod) 
p_direction(types_mod, effects="all") # cage 78, cond*age 83%

e1_lexdiv <- e1ld %>% group_by(condition) %>%
  summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) # types=mean(types) # con=16.7, exp=18.1
```

```{r, e1ld-exploratory, echo=F, include=F}
# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
e1model_string = "~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video)"
# only 54 parents completed the EPAQ

modTTRE <- stan_glmer(paste("TTR", e1model_string), data=e1ld)
summary(modTTRE) 
p_direction(modTTRE, effects="all") # RR 87%  parent_ed 90.9%

modMTLDE <- stan_glmer(paste("MTLD", e1model_string), data=e1ld)
summary(modMTLDE) #
p_direction(modMTLDE, effects="all") # genderM 85%, RR 85%, AA 77%..

tokens_modE <- stan_glmer(paste("tokens", e1model_string),  data=e1ld) 
summary(tokens_modE) # condition 54.4 
get_stan_glmer_reporting_values(tokens_modE, 'parent_ed') # 
p_direction(tokens_modE, effects="all") # RR 73.5% parent_ed 90.5%

# predict word types
types_modE <- stan_glmer(paste("types", e1model_string), data=e1ld) 
summary(types_modE) 
p_direction(types_modE, effects="all") # EL 84% AA 79% genderM 79%, parent_ed 89% cond:AA 96.3%
e1types_condAA = get_stan_glmer_reporting_values(types_modE, 'conditionexp:AA') # ADD THIS TO TEXT

```

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
For effects that are at least 95% likely to be non-zero according to the posterior distribution (i.e., probability of direction: *pd*; @Makowski2019), we report estimated coefficients ($\beta$) as well as 89% Bayesian credible intervals (89% CI)[^4], demarcating the range within which 89% of the posterior falls, meaning that given the observed data, the effect has 89% probability of falling within this range (see Appendix for more an illustrated explanation).
There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, `r print_CI(e1TTR)`). 
A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, `r print_CI(e1MTLD)`), with no notable influence of age.
Figure \ref{fig:lexdiv} (top) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

```{r e1tokens, echo=F, include=F}
e1ld$Condition = factor(e1ld$condition, levels = c("con", "exp"), labels = c("No Video", "Activity Video"))

e1_mtld <- e1ld %>% group_by(Condition) %>%
  tidyboot_mean(MTLD) 
e1_lex <- e1ld %>% group_by(Condition) %>%
  tidyboot_mean(TTR) # Type/Token Ratio
e1_tok <- e1ld %>% group_by(Condition) %>%
  tidyboot_mean(tokens) 
e1_type <- e1ld %>% group_by(Condition) %>%
  tidyboot_mean(types)
```

We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding a notable effect of condition on the rate of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, `r print_CI(e1tokens)`), with parents using tokens at a higher rate in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)` tokens/min, bootstrapped 95% confidence interval (conf. int.): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`, `r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, 95% conf. int.: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`, `r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).

```{r e1tab, echo=F, include=F}
e1 <- e1ld %>% group_by(Condition) %>%
  summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
            "Mean MTLD"=mean(MTLD), MTLDsd=sd(MTLD),
            "Mean types"=mean(types), types.sd=sd(types),
            "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
names(e1) = c("Condition","TTR/min (M)", "(sd)", "MTLD/min (M)", "(sd)", "Types/min (M)", "(sd)", "Tokens/min (M)", "(sd)")
kable(e1, digits=2, caption="Lexical diversity measures in Experiment 1.")
```

```{r e1ld-figs, include=F}
small_text = theme(
  plot.title = element_text(size = 12, face="bold"),
  axis.title.x = element_text(size = 10),
  axis.text.x = element_text(size = 8),
  axis.title.y = element_text(size = 10),
  axis.text.y = element_text(size = 8))

e1ttr <- ggplot(e1_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .7)) +
  geom_point(data=e1ld, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle("Experiment 1") + small_text
# want carriage return in Condition labels..

e1mtld <- ggplot(e1_mtld, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ld, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("MTLD") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle(" ") + small_text

e1tokens <- ggplot(e1_tok, aes(x=Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ld, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Mean Word Tokens per Minute") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

```

```{r fig-lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=5.5, fig.cap = "\\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition (right) in Experiment 1 (top) and Experiment 2 (bottom). Error bars show bootstrapped 95\\% confidence intervals, and gray dots indicate values for each participant."}

ttr2 <- e2ld %>% group_by(Condition) %>%
  tidyboot_mean(TTR)

e2ttr <- ggplot(ttr2, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + # labels=addline_format(c("Science Video", "Activity Video"))
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2ld, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle("Experiment 2") + small_text

mtld2 <- e2ld %>% group_by(Condition) %>%
  tidyboot_mean(MTLD)

e2mtld <- ggplot(mtld2, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2ld, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("MTLD") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

e2tok <- e2ld %>% group_by(Condition) %>%
  tidyboot_mean(tokens)

e2tokens <- ggplot(e2tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2ld, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Mean Word Tokens per Minute") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

#multiplot(e1ttr, e1mtld, e1tokens, cols=3) # Exp1 LD graph
#multiplot(e2ttr, e2mtld, e2tokens, cols=3) # Exp2 LD graph

multiplot(e1ttr, e1mtld, e1tokens, 
          e2ttr, e2mtld, e2tokens, cols=3, layout=matrix(c(1,2,3, 4,5,6), nrow=2, byrow=T)) 
```

```{r, e1-effect-size, echo=F, include=F}
cohens_d <- function(dat) {
  return( diff(dat$mean) / (sqrt(sum(dat$sd^2)) / 2) )
}

ttr_means <- e1ld %>% group_by(Condition) %>%
  summarise(mean = mean(TTR), sd = sd(TTR))
cohens_d(ttr_means) # -1.68 - should we report this?
```

### Joint Attention

```{r, e1ja-regressions, echo=F, include=F}

model_string = "~ Condition * age + (1| Video)" # + gender + parent_ed
# Total number of bids
e1bids_mod <- stan_glmer(paste("bids_tot", model_string), data = e1ja, adapt_delta = .98) # 
summary(e1bids_mod) 
p_direction(e1bids_mod, effects="all") # condition
e1bids = get_stan_glmer_reporting_values(e1bids_mod, "ConditionActivity Video") # .72

e1bids_M <- e1ja %>% group_by(Condition) %>% 
  summarise(mean = mean(bids), sd = sd(bids))

# Episodes of passive joint attention.
e1pja_mod <- stan_lmer(paste("pja", model_string), data = e1ja)
summary(e1pja_mod) # NA
p_direction(e1pja_mod, effects="all") # condition 89%

# Episodes of coordinated joint attention.
e1cja_mod <- stan_lmer(paste("cja", model_string), adapt_delta = 0.99, data = e1ja) 
summary(e1cja_mod) # NA
p_direction(e1cja_mod, effects="all") # condition 81%

# Total duration of passive joint attention.
e1pja_time_mod <- stan_lmer(paste("pja_length", model_string), data = e1ja, adapt_delta=.98)
summary(e1pja_time_mod) # NA
p_direction(e1pja_time_mod, effects="all") # condition 90.6%

# Total duration of coordinated joint attention.
e1cja_time_mod <- stan_lmer(paste("cja_length", model_string), data = e1ja)
summary(e1cja_time_mod) # NA
p_direction(e1cja_time_mod, effects="all") # cond*age 86%
```

We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video. 
Parents' bid rate was greater in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, `r print_CI(e1bids)`). 
Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA.
There were no notable effects on the rate of episodes nor on the time spent in coordinated or passive JA episodes.
Figure \ref{fig:JA} (top) shows the mean rate of bids and episodes of JA by condition in Experiment 1.

### Exploratory Analyses

```{r e1ja-epaq-regressions, include=F, echo=F}
# follow-up regression (if we find a sig effect?)
model_stringE =  "~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed + (1| Video)"

# Rate of parental bids
e1bids_modE <- stan_glmer(paste("bids_tot", model_stringE), data = e1ja) 
summary(e1bids_modE) # cond, gender 
p_direction(e1bids_modE, effects="all")
e1bidsE = get_stan_glmer_reporting_values(e1bids_modE, "genderM") # .73 [.11,1.36] REPORT

e1bidsE_M <- e1ja %>% group_by(gender) %>% 
  summarise(mean = mean(bids), sd = sd(bids))

# Episodes of coordinated joint attention.
e1cja_modE <- stan_lmer(paste("cja", model_stringE), data = e1ja)
p_direction(e1cja_modE, effects="all") # RR 89% parent_ed 89%
summary(e1cja_modE) # NA

# Episodes of passive joint attention.
e1pja_modE <- stan_lmer(paste("pja", model_stringE), data = e1ja)
summary(e1pja_modE) # condition*RR beta=1.8, RR close
p_direction(e1pja_modE, effects="all") # RR 98%, parent_ed 98%
e1pjaRR = get_stan_glmer_reporting_values(e1pja_modE, "RR") # -.34, 89% CI = [-.65,-.02]  
e1pjaE = get_stan_glmer_reporting_values(e1pja_modE, "ConditionActivity Video:RR") # .60 [.14,1.05]
e1pja_parent_ed = get_stan_glmer_reporting_values(e1pja_modE, "parent_ed")

# Total duration of passive joint attention.
e1pja_time_modE <- stan_lmer(paste("pja_length", model_stringE), data = e1ja)
summary(e1pja_time_modE) # NA
p_direction(e1pja_time_mod, effects="all") # condition 91%

# Total duration of coordinated joint attention.
e1cja_time_modE <- stan_lmer(paste("cja_length", model_stringE), data = e1ja)
summary(e1cja_time_modE) # NA
p_direction(e1cja_time_mod, effects="all") # condition:age 86%
```

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), the child's sex, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR. 
These models included random intercepts per video. 
Of these exploratory regressions, two showed notable effects involving the EPAQ subscales, and one other showed an effect of the child's sex.
First, in the word types regression, parents with higher Affection and Attachment scores used more word types per minute after watching an Activity Video (interaction of condition and AA: $\beta=`r e1types_condAA["conditionexp:AA"]`$, `r print_CI(e1types_condAA)`).
Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes ($\beta=`r e1pjaRR["RR"]`$, `r print_CI(e1pjaRR)`). 
However, after an Activity Video, higher RR parents did not show this decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, `r print_CI(e1pjaE)`). 
Parents with higher education also showed a lower rate of passive JA episodes ($\beta=`r e1pja_parent_ed['parent_ed']`$, `r print_CI(e1pja_parent_ed)`).
Finally, parents with male children made bids for JA at a higher rate (mean: `r round(e1bidsE_M[2,]$mean,2)` bids/min) than those with female children (mean: `r round(e1bidsE_M[1,]$mean,2)`, $\beta=`r e1bidsE["genderM"]`$, `r print_CI(e1bidsE)`).

To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list ([see SI](https://osf.io/2bpdf/files/github/language_analyses/Exp1_characteristic_chart.html) for the interactive corpus characteristic plot). 
Words that were strongly indicative of being from the Activity Video condition include "give", "big", "small", "ribbit", "thank", "have", and "bus", while words that were most characteristic of the No Video condition include "shake", "ready", "oh", "on", "going", "going", "see", "let", and the child's name.

```{r fig-JA, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=5.5, fig.cap = "\\label{fig:JA} Mean number of bids (left) and episodes (right) of joint attention (JA) by condition in Experiment 1 (top). For Experiment 2 (bottom), mean number of bids for JA by condition (left) and the number of episodes of JA by age and condition (right)."}
# Parents made significantly more bids for JA after watching an activity video, but this did not result in a greater number of episodes of JA.

ms_bids1 <- e1ja %>% group_by(Condition) %>%
  tidyboot_mean(bids_tot)

e1bids <- ggplot(ms_bids1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ja, aes(x=Condition, y=bids_tot), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Parental Bids for JA per Minute") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle("Experiment 1") + small_text

# total joint attention episodes
ms_tja1 <- e1ja %>% group_by(Condition) %>%
  tidyboot_mean(total_ja)

>>>>

---
title: "Untitled"
author: "George Kachergis"
date: "4/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@
